A better way to format your document for CEUR-WS

### 2024-05-27 paper/paper-part2.tex
why did we choose TinyBert

From~\cite{jiao20}: Language model pre-training, such as BERT, has significantly improved the performances of many natural language processing tasks. However, pre-trained language models are usually computationally expensive, so it is difficult to efficiently execute them on resource-restricted devices. To accelerate inference and reduce model size while maintaining accuracy, we first propose a novel Transformer distillation method that is specially designed for knowledge distillation (KD) of the Transformer-based models. By leveraging this new KD method, the plenty of knowledge encoded in a large teacher BERT can be effectively transferred to a small student Tiny-BERT. Then, we introduce a new two-stage learning framework for TinyBERT, which performs Transformer distillation at both the pretraining and task-specific learning stages. This framework ensures that TinyBERT can capture he general-domain as well as the task-specific knowledge in BERT.
TinyBERT with 4 layers is empirically effective and achieves more than 96.8\% the performance of its teacher BERTBASE on GLUE benchmark, while being 7.5x smaller and 9.4x faster on inference. TinyBERT with 4 layers is also significantly better than 4-layer state-of-the-art baselines on BERT distillation, with only about 28\% parameters and about 31\% inference time of them. Moreover, TinyBERT with 6 layers performs on-par with its teacher BERTBASE.

>>>>

From~\cite{jiao20}: TinyBERT offers several advantages over other models, especially when it comes to efficiency and performance. One of the primary benefits is its reduced size and faster inference time. TinyBERT4, which comprises only four layers, is 7.5 times smaller and 9.4 times faster than its teacher model, BERTBASE. Despite this significant reduction in size, TinyBERT4 achieves more than 96.8\% of the performance of BERTBASE on the GLUE benchmark tasks, demonstrating that it can maintain high accuracy while being substantially more efficient. This makes TinyBERT particularly suitable for applications on resource-restricted devices where computational power and memory are limited.

Furthermore, TinyBERT employs a novel two-stage learning framework that involves both general distillation and task-specific distillation. In the general distillation stage, TinyBERT learns from the original BERT model without fine-tuning, capturing general domain knowledge. Subsequently, task-specific distillation is performed using fine-tuned BERT, allowing TinyBERT to absorb knowledge tailored to specific tasks. This two-stage process ensures that TinyBERT not only inherits the rich, general knowledge from BERT but also hones its performance on specific tasks, thereby improving its adaptability and effectiveness in various natural language processing tasks.

Moreover, TinyBERT's distillation process includes advanced techniques such as attention-based and hidden states-based distillation. These techniques are designed to transfer the linguistic knowledge encoded in the teacher model's attention weights and hidden states to the student model. This method helps TinyBERT retain essential linguistic features, which are crucial for tasks involving syntax and coreference resolution. The complementary nature of these distillation methods ensures that TinyBERT can achieve high performance even with fewer parameters and reduced computational requirements.

Finally, TinyBERT demonstrates superior performance compared to other state-of-the-art models designed for model compression. For instance, TinyBERT4 significantly outperforms other 4-layer models like BERT4-PKD and DistilBERT4 by at least 4.4\%, while using only about 28\% of the parameters and 31\% of the inference time of these models . When scaled up to six layers, TinyBERT6 achieves performance on par with BERTBASE, making it a robust and scalable solution for diverse NLP tasks. These benefits collectively highlight why TinyBERT is an excellent choice for applications requiring efficient and high-performing language models.\\
